Incentivizing Exploration with Unbiased History

### 2018-10-28 llevel-overview.tex

Now we give some overview of the additional techniques we use to get our $L$-level results.

\xhdr{New connecting structures between levels.}

>>>>

The main idea of extending from 3-level to $L$-level is that instead of using the second level as one ``check-point'', we use more levels to have multiple ``check points''.  Some new challenges appear in this process. Here give an overview of the additional techniques we use to get our $L$-level results.

\xhdr{Connecting structures between levels.} In our 3-level policy, the second level has $S = \Theta(\log(T))$ groups. We do so to ensure that in the small gap case, with high probability, both arms are pulled enough times in the second level. The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantee each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.

Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure in the info graph. It incurs an extra $S^L$ factor in the expected regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor would be $\Omega\left(\log(T)^{\log\log(T)}\right)$ which is super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

In order to avoid this undesirable factor, we design a slightly different connecting structure in our $L$-level policy. The key observation is that, for any level $l \in \{3,...,L-1\}$, we do want agents in different $l$-th level groups to see disjoint histories of the $(l-1)$-th level to ensure that there is some ``lucky'' group for each arm $a$ when arm $a$'s mean is close enough to the best arm. However, it does not matter much if these agents see the same history of levels below $l-1$ because group sizes in lower levels are much smaller than group sizes in higher levels and the independent randomness in level $l-1$ is sufficient.

### 2018-10-28 llevel.tex
llevel theorems

\section{$L$-level Recommendation Policy}
\label{sec:llevel-details}
In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.

@@

\begin{theorem}
Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} can be extended to the case when $K$ is constant larger than 2. In the extension of Corollary \ref{cor:llevel}, $\Delta$ is defined as the difference between means of the best and the second best arm.
\end{theorem}

>>>>

\section{Missing Proofs of Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design an $L$-level recommendation policy for $L > 3$ and 2 arms. By having more than 3 levels, we get even smaller regret.

@@

\begin{theorem}
\label{thm:constarm}
Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} can be extended to the case when $K$ is constant larger than 2. In the extension of Corollary \ref{cor:llevel}, $\Delta$ is defined as the difference between means of the best and the second best arm.
\end{theorem}
